Minimizing post-shock forecasting error using disparate information

### 2020-08-19 manuscript/comp.tex
edits to typos and unclear points, major edits to Section 3.2 and Section 5

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (498.49,111.84) {$\hat{y}^{1}_{T_1^*+1} = 0.46$};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (492.81, 70.86) {shock time point $T^*_1 + 1$};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (364.99,179.57) {$y_{T_1^*+1}$};
\definecolor{drawColor}{RGB}{255,0,255}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (335.16,205.47) {$\hat{y}^{2}_{T_1^*+1}=\hat{y}^{1}_{T_1^*+1} + \hat{\alpha}$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (379.19,207.97) -- (427.48,207.97);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (423.10,205.44) --
	(427.48,207.97) --
	(423.10,210.50);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (379.19,182.07) -- (427.48,182.07);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (423.10,179.54) --
	(427.48,182.07) --
	(423.10,184.60);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 66.75,207.97) rectangle (212.08,171.97);
\definecolor{drawColor}{RGB}{255,106,106}

\path[draw=drawColor,line width= 0.8pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] ( 75.75,195.97) -- ( 93.75,195.97);
\definecolor{drawColor}{RGB}{255,0,255}

\path[draw=drawColor,line width= 0.8pt,dash pattern=on 1pt off 3pt ,line join=round,line cap=round] ( 75.75,183.97) -- ( 93.75,183.97);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (102.75,192.53) {$\hat{y}_{t}^{1}$ without shock effects};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (102.75,180.53) {$\hat{y}_{t}^{2}$ with shock effects};
\end{scope}
\end{tikzpicture}

>>>>

\node[text=drawCo sep=0pt, outer sep=0pt, scale=  1.00] at (470.08,425.61) {$\alpha = 4.21$};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (492.81,372.18) {shock time point $T^*_1 + 1$};

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (364.99,472.53) {$y_{T_1^*+1}$};
\definecolor{drawColor}{RGB}{255,0,255}

\node[text=drawColor,anchor=base,inner sep=0pt, outer sep=0pt, scale=  1.00] at (335.16,513.81) {$\hat{y}^{2}_{T_1^*+1}=\hat{y}^{1}_{T_1^*+1} + \hat{\alpha}$};

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (379.19,516.31) -- (427.48,516.31);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (423.10,513.78) --
	(427.48,516.31) --
	(423.10,518.84);
\definecolor{drawColor}{RGB}{0,0,0}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (379.19,475.03) -- (427.48,475.03);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (423.10,472.50) --
	(427.48,475.03) --
	(423.10,477.56);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] ( 66.75,516.31) rectangle (212.08,480.31);
\definecolor{drawColor}{RGB}{255,106,106}

\path[draw=drawColor,line width= 0.8pt,dash pattern=on 4pt off 4pt ,line join=round,line cap=round] ( 75.75,504.31) -- ( 93.75,504.31);
\definecolor{drawColor}{RGB}{255,0,255}

\path[draw=drawColor,line width= 0.8pt,dash pattern=on 1pt off 3pt ,line join=round,line cap=round] ( 75.75,492.31) -- ( 93.75,492.31);
\definecolor{drawColor}{RGB}{0,0,0}

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (102.75,500.87) {$\hat{y}_{t}^{1}$ without shock effects};

\node[text=drawColor,anchor=base west,inner sep=0pt, outer sep=0pt, scale=  1.00] at (102.75,488.87) {$\hat{y}_{t}^{2}$ with shock effects};
\end{scope}
\end{tikzpicture}

\end{document}
}
\end{tikzpicture}

### 2020-08-19 manuscript/fig2.tex
edits to typos and unclear points, major edits to Section 3.2 and Section 5

% Created by tikzDevice version 0.12.3 on 2020-06-28 18:03:01
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{tikz}

@@

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (479.09, 91.25) --
	(481.73, 86.67) --
	(476.44, 86.67) --
	(479.09, 91.25);
\definecolor{drawColor}{RGB}{0,191,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (476.31, 88.07) -- (481.86, 88.07);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (479.09, 85.29) -- (479.09, 90.84);
\definecolor{drawColor}{RGB}{238,99,99}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (477.12, 81.21) -- (481.05, 85.13);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (477.12, 85.13) -- (481.05, 81.21);
\definecolor{drawColor}{RGB}{238,130,238}
\definecolor{fillColor}{RGB}{238,130,238}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (479.09,141.49) circle (  1.96);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 66.76,313.70) --
	( 80.50,313.67) --
	( 94.25,302.10) --
	(107.99,304.27) --
	(121.74,297.06) --
	(135.48,299.42) --
	(149.23,290.97) --
	(162.97,283.99) --
	(176.71,258.33) --
	(190.46,290.13) --
	(204.20,281.01) --
	(217.95,276.50) --
	(231.69,274.52) --
	(245.43,289.86) --
	(259.18,300.87) --
	(272.92,286.25) --
	(286.67,282.81) --
	(300.41,276.99) --
	(314.16,288.22) --
	(327.90,280.06) --
	(341.64,273.21) --
	(355.39,252.42) --
	(369.13,229.35) --
	(382.88,199.60) --
	(396.62,163.01) --
	(410.37,175.15) --
	(424.11,190.38) --
	(437.85,181.33) --
	(451.60,180.97) --
	(465.34,175.47) --
	(479.09,141.49);
\definecolor{drawColor}{RGB}{0,0,0}

>>>>

% Created by tikzDevice version 0.12.3.1 on 2020-08-19 16:49:26
% !TEX encoding = UTF-8 Unicode
\documentclass[10pt]{article}
\usepackage{tikz}

@@

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (479.09, 99.95) --
	(481.73, 95.38) --
	(476.44, 95.38) --
	(479.09, 99.95);
\definecolor{drawColor}{RGB}{0,191,255}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (476.31,101.69) -- (481.86,101.69);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (479.09, 98.92) -- (479.09,104.47);
\definecolor{drawColor}{RGB}{238,99,99}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (477.12, 95.61) -- (481.05, 99.53);

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round] (477.12, 99.53) -- (481.05, 95.61);
\definecolor{drawColor}{RGB}{238,130,238}
\definecolor{fillColor}{RGB}{238,130,238}

\path[draw=drawColor,line width= 0.4pt,line join=round,line cap=round,fill=fillColor] (479.09,144.69) circle (  1.96);

\path[draw=drawColor,line width= 0.6pt,line join=round] ( 66.76,323.78) --
	( 80.50,312.48) --
	( 94.25,297.05) --
	(107.99,301.43) --
	(121.74,296.20) --
	(135.48,301.14) --
	(149.23,292.29) --
	(162.97,286.87) --
	(176.71,273.08) --
	(190.46,289.26) --
	(204.20,285.58) --
	(217.95,276.06) --
	(231.69,276.86) --
	(245.43,287.14) --
	(259.18,290.90) --
	(272.92,284.54) --
	(286.67,282.37) --
	(300.41,275.05) --
	(314.16,282.80) --
	(327.90,275.49) --
	(341.64,276.64) --
	(355.39,253.30) --
	(369.13,224.73) --
	(382.88,201.68) --
	(396.62,172.73) --
	(410.37,172.62) --
	(424.11,200.63) --
	(437.85,172.58) --
	(451.60,180.66) --
	(465.34,165.66) --
	(479.09,144.69);
\definecolor{drawColor}{RGB}{0,0,0}
